THESIS PROJECT PROPOSAL

### 2019-11-07 project_ashish/paper.tex
commit

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms5.png}
  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quarks decaying to W boson and bottom quark, W boson decaying to leptons.}
   \label{figure 7}
\end{figure}

@@

The production of Higgs boson in association with single top quark is one of the rare Higgs 
boson production mode. As the top 
quark is the heaviest fundamental particle in the standard model, due to its large mass, the 
top quark decay before 
hardronization which allow the possibility to reconstruct top quark from its decay products 
unlike the lighter quarks which 
undergo hardronization and are seen as bundles of particles in detector called jets. The most 
probable decay of top quark is 
into bottom (b) quark and W boson \cite{nishiwaki2014tth}. Using b-jet tagging algorithms, the jet originating from 
b-quark can be reconstructed to 
identity the top quark. In SM, the coupling of the Higgs boson to fermions like quarks and 
leptons is proportional to the mass 
of the fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson 
which means that out of all known 
quarks, top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa 
coupling $y_t$. That is why the 
Yukawa coupling of the top quark with the Higgs boson $y_t$ has lot of importance as any 
deviation from standard model prediction might give an indication of new physics. The two 
processes at LHC which will allow us to directly probe the Yukawa 
coupling between Higgs Boson and top quark are Higgs boson production in association with top 
quark pair (t$\bar{t}$H) via 
strong interaction and the production of single top quark with a Higgs boson (tH). As tH 
occur via electroweak interaction, it 
is more rare than t$\bar{t}$H production. The Higgs boson in the tH channel can be radiated 
off by a W boson or by a top 
quark. These two processes in standard model have destructive interference which allow us to 
probe the relative sign between 
the coupling of top quark with Higgs boson $y_t$ and the coupling of W boson to the Higgs 
boson. If the Yukawa coupling between top quark and Higgs boson $y_t$ deviate from the SM 
prediction or even if $y_t$ has a negative sign, both would cause a strong increase in the tH 
production cross section which is a special property of tH production channel making it an 
interesting production channel to probe using LHC 2016, 2017 and 2018 data. The coupling 
strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 
us the deviation of $y_t$ from the SM prediction \cite{sirunyan2019search}. 
The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top 
quark associated production mode. 
The anomalous coupling will arise when we add interaction terms (dimension 6 operators in 
effective SM theory) in the Higgs 
potential. As there is strong destructive inteference in the t-channel for the standard model 
couplings, this production mode 
is sensitive to both the sign and the magnitude of any coupling beyond the SM between Higgs 
boson and top quark induced by 
higher dimensional operators in effective SM theory.

>>>>

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/cms5.png}
  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quarks decaying to W boson and bottom quark, W boson decaying to leptons.}
   \label{figure 7}
\end{figure}

@@

The production of Higgs boson in association with single top quark is one of the rare Higgs 
boson production mode \cite{Khachatryan_2016}. As the top 
quark is the heaviest fundamental particle in the standard model, due to its large mass, the 
top quark decay before 
hardronization which allow the possibility to reconstruct top quark from its decay products 
unlike the lighter quarks which 
undergo hardronization and are seen as bundles of particles in detector called jets. The most 
probable decay of top quark is 
into bottom (b) quark and W boson \cite{nishiwaki2014tth}. Using b-jet tagging algorithms, the jet originating from 
b-quark can be reconstructed to 
identity the top quark. In SM, the coupling of the Higgs boson to fermions like quarks and 
leptons is proportional to the mass 
of the fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson 
which means that out of all known 
quarks, top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa 
coupling $y_t$. That is why the 
Yukawa coupling of the top quark with the Higgs boson $y_t$ has lot of importance as any 
deviation from standard model prediction might give an indication of new physics. The two 
processes at LHC which will allow us to directly probe the Yukawa 
coupling between Higgs Boson and top quark are Higgs boson production in association with top 
quark pair (t$\bar{t}$H) via 
strong interaction and the production of single top quark with a Higgs boson (tH). As tH 
occur via electroweak interaction, it 
is more rare than t$\bar{t}$H production \cite{sirunyan2018search}. The Higgs boson in the tH channel can be radiated 
off by a W boson or by a top 
quark. These two processes in standard model have destructive interference which allow us to 
probe the relative sign between 
the coupling of top quark with Higgs boson $y_t$ and the coupling of W boson to the Higgs 
boson \cite{choudhury2019search}. If the Yukawa coupling between top quark and Higgs boson $y_t$ deviate from the SM 
prediction or even if $y_t$ has a negative sign, both would cause a strong increase in the tH 
production cross section which is a special property of tH production channel making it an 
interesting production channel to probe using LHC 2016, 2017 and 2018 data. The coupling 
strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 
us the deviation of $y_t$ from the SM prediction. 
The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top 
quark associated production mode. 
The anomalous coupling will arise when we add interaction terms (dimension 6 operators in 
effective SM theory) in the Higgs 
potential. As there is strong destructive inteference in the t-channel for the standard model 
couplings, this production mode 
is sensitive to both the sign and the magnitude of any coupling beyond the SM between Higgs 
boson and top quark induced by 
higher dimensional operators in effective SM theory \cite{sirunyan2019search}.
